Spike-and-Slab Generalized Additive Models and Scalable Algorithms for High-Dimensional Data

### 2022-03-21 Manuscript/00-main.Rmd
Revise caption

```{r }
tbl_real_time %>% 
  flextable::set_caption(caption = "Model fitting time in seconds for two metabolomics data analyses, from Emory Cardiovascular Biobank (ECB) and Weight Loss Maintenance Cohort (WLM). It tabulates the computation time for cross-validation step (CV) and optimal model fitting step (Final), and total computation time (Total) for the proposed model BHAM with EM-CD algorithm (BHAM-CD) and the model of comparison SB-GAM.")
```
\label{tab:time_real_data}

>>>>

```{r }
tbl_real_time %>% 
  flextable::set_caption(caption = "Model fitting time in seconds for two metabolomics data analyses, from Emory Cardiovascular Biobank (ECB) and Weight Loss Maintenance Cohort (WLM). It tabulates the computation time for cross-validation step (CV) and optimal model fitting step (Final), and total computation time (Total) for the proposed model BHAM and the model of comparison SB-GAM.")
```
\label{tab:time_real_data}

### 2022-03-21 Manuscript/03-Simulation.Rmd
Revise caption

\bg{\subsubsection{Variable Selection Performance}}
\bg{Among the set of simulations where the functional forms of the predictors are nonlinear, the proposed model, BHAM, has a consistent performance across different dimension and distribution settings (See Table \ref{sec:gaus_var_select} for Gaussian outcomes, and Support Information Table S3 for binomial outcomes): being conservative. The symptoms of conservative variable selection are high precision and low recall, where high precision means that among all the selected variables, high percentage of them are true signals; low recall means that, the model selected small subset among all the active predictions. In other words, BHAM tends to select a smaller set of variables that are truly effective to the outcome. We want to note, the variable selection performance of BHAM is plummeted and not optimized when $p=200$. Upon further investigation, we discover it's because the generic sequence of $s_0$ used to tune the model doesn't contain the optimal value. Overall, among all the models examined, SB-GAM has the best performance, both high precision and high recall, and yield a high MCC. The performance of another Bayesian model, spikeSlabGAM deteriorates as the sparsity grows, particularly when ($p>50$), or for binomial outcomes. The variable selection performance for linear simulations match with prediction performance: BHAM performs great among the Gaussian scenarios, while the performance of SB-GAM deteriorates.}

>>>>

\bg{\subsubsection{Variable Selection Performance}}
\bg{Among the set of simulations where the functional forms of the predictors are nonlinear, the proposed model, BHAM, has a consistent performance across different dimension and distribution settings (See Table \ref{tab:sim_gaus_var_select} for Gaussian outcomes, and Support Information Table S3 for binomial outcomes): being conservative. The symptoms of conservative variable selection are high precision and low recall, where high precision means that among all the selected variables, high percentage of them are true signals; low recall means that, the model selected small subset among all the active predictions. In other words, BHAM tends to select a smaller set of variables that are truly effective to the outcome. We want to note, the variable selection performance of BHAM is plummeted and not optimized when $p=200$. Upon further investigation, we discover it's because the generic sequence of $s_0$ used to tune the model doesn't contain the optimal value. Overall, among all the models examined, SB-GAM has the best performance, both high precision and high recall, and yield a high MCC. The performance of another Bayesian model, spikeSlabGAM deteriorates as the sparsity grows, particularly when ($p>50$), or for binomial outcomes. The variable selection performance for linear simulations match with prediction performance: BHAM performs great among the Gaussian scenarios, while the performance of SB-GAM deteriorates.}

### 2022-03-21 Manuscript/SS_GAM.tex
Revise caption

\textcolor{red}{\subsubsection{Variable Selection Performance}}
\textcolor{red}{Among the set of simulations where the functional forms of the predictors are nonlinear, the proposed model, BHAM, has a consistent performance across different dimension and distribution settings (See Table \ref{sec:gaus_var_select} for Gaussian outcomes, and Support Information Table S3 for binomial outcomes): being conservative. The symptoms of conservative variable selection are high precision and low recall, where high precision means that among all the selected variables, high percentage of them are true signals; low recall means that, the model selected small subset among all the active predictions. In other words, BHAM tends to select a smaller set of variables that are truly effective to the outcome. We want to note, the variable selection performance of BHAM is plummeted and not optimized when $p=200$. Upon further investigation, we discover it's because the generic sequence of $s_0$ used to tune the model doesn't contain the optimal value. Overall, among all the models examined, SB-GAM has the best performance, both high precision and high recall, and yield a high MCC. The performance of another Bayesian model, spikeSlabGAM deteriorates as the sparsity grows, particularly when ($p>50$), or for binomial outcomes. The variable selection performance for linear simulations match with prediction performance: BHAM performs great among the Gaussian scenarios, while the performance of SB-GAM deteriorates.}

@@

\caption{Model fitting time in seconds for two metabolomics data analyses, from Emory Cardiovascular Biobank (ECB) and Weight Loss Maintenance Cohort (WLM). It tabulates the computation time for cross-validation step (CV) and optimal model fitting step (Final), and total computation time (Total) for the proposed model BHAM with EM-CD algorithm (BHAM-CD) and the model of comparison SB-GAM.
}\\

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2.25in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{BHAM-CD}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2.25in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{SB-GAM}}} \\

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{WLM}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{365.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{6.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{371.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,116.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{32.7}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,148.7}}} \\

>>>>

\textcolor{red}{\subsubsection{Variable Selection Performance}}
\textcolor{red}{Among the set of simulations where the functional forms of the predictors are nonlinear, the proposed model, BHAM, has a consistent performance across different dimension and distribution settings (See Table \ref{tab:sim_gaus_var_select} for Gaussian outcomes, and Support Information Table S3 for binomial outcomes): being conservative. The symptoms of conservative variable selection are high precision and low recall, where high precision means that among all the selected variables, high percentage of them are true signals; low recall means that, the model selected small subset among all the active predictions. In other words, BHAM tends to select a smaller set of variables that are truly effective to the outcome. We want to note, the variable selection performance of BHAM is plummeted and not optimized when $p=200$. Upon further investigation, we discover it's because the generic sequence of $s_0$ used to tune the model doesn't contain the optimal value. Overall, among all the models examined, SB-GAM has the best performance, both high precision and high recall, and yield a high MCC. The performance of another Bayesian model, spikeSlabGAM deteriorates as the sparsity grows, particularly when ($p>50$), or for binomial outcomes. The variable selection performance for linear simulations match with prediction performance: BHAM performs great among the Gaussian scenarios, while the performance of SB-GAM deteriorates.}

@@

\caption{Model fitting time in seconds for two metabolomics data analyses, from Emory Cardiovascular Biobank (ECB) and Weight Loss Maintenance Cohort (WLM). It tabulates the computation time for cross-validation step (CV) and optimal model fitting step (Final), and total computation time (Total) for the proposed model BHAM and the model of comparison SB-GAM.
}\\

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2.25in+4\tabcolsep+2\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{BHAM}}} & \multicolumn{3}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 2.25in+4\tabcolsep+2\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{SB-GAM}}} \\

@@

\multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{WLM}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{365.4}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{6.8}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{372.2}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,116.0}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{32.7}}} & \multicolumn{1}{!{\color[HTML]{000000}\vrule width 0pt}>{\centering}p{\dimexpr 0.75in+0\tabcolsep+0\arrayrulewidth}!{\color[HTML]{000000}\vrule width 0pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{000000}{3,148.7}}} \\
